---
title: "Developing Data Products Week 3 Assignment"
author: "Papachrysanthou George"
date: "May 20, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plotly)
```

## Countries power production capacity

Power production capacity per country vs population and GDP per capita. Radius ~ power production capacity, Color ~ power production capacity / population

```{r echo = FALSE, warning=FALSE}

global_power_plants = read.csv("E:/GPAPAC_Files/Study/Coursera/09.DevelopingDataProducts/Week3Assignment/globalpowerplantdatabasev100/global_power_plant_database.csv", dec=".", na.strings = "NA",stringsAsFactors=FALSE)

countries_population<-read.csv("E:/GPAPAC_Files/Study/Coursera/09.DevelopingDataProducts/Week3Assignment/globalpowerplantdatabasev100/API_SP.POP.TOTL_DS2_en_csv_v2_9908626.csv",stringsAsFactors=FALSE, skip = 4, header = T, dec=".")

countries_percapitaGDP<-read.csv("E:/GPAPAC_Files/Study/Coursera/09.DevelopingDataProducts/Week3Assignment/globalpowerplantdatabasev100/API_NY.GDP.PCAP.CD_DS2_en_csv_v2_9908784.csv",stringsAsFactors=FALSE, skip = 4, header = T, dec=".")


countries_population2015 <- countries_population[,c("Country.Code", "Country.Name", "X2015")]

names(countries_population2015)[3] <- "Population"

countries_percapitaGDP2015 <- countries_percapitaGDP[,c("Country.Code", "X2015")]

names(countries_percapitaGDP2015)[2] <- "PerCapitaGDP"


countries_data <- merge(countries_population2015, countries_percapitaGDP2015, by.x=c("Country.Code"), by.y=c("Country.Code"))

# str(countries_data)
# str(global_power_plants)
# str(countries_population2015)

mw_by_country_and_fuel1 <- aggregate(capacity_mw ~ country + fuel1, data=global_power_plants, FUN=sum)

mw_by_country <- aggregate(capacity_mw ~ country, data=global_power_plants, FUN=sum)

mw_by_country$capacity_gw <- mw_by_country$capacity_mw/1000 

mw_by_country_new <- merge(mw_by_country, countries_data, by.x=c("country"), by.y=c("Country.Code"))

mw_by_country_new$capacity_kw_per_capita <- 1000*mw_by_country_new$capacity_mw / mw_by_country_new$Population

# str(mw_by_country_new)

# power_plants_lat_long <- data.frame(lat=global_power_plants$latitude, lng=global_power_plants$longitude )

# power_plants_popup<-global_power_plants$name

# my_map<-power_plants_lat_long %>% leaflet() %>% addTiles() %>% addCircleMarkers(popup=power_plants_popup, weight=1, radius=3, color="green")
# my_map


# plot_ly(mw_by_country_new, x=~Population, y=~PerCapitaGDP, z=~capacity_mw, type="scatter3d", mode="markers")

plot_ly(mw_by_country_new, x=~Population, y=~PerCapitaGDP, type = 'scatter', mode="markers", color=~capacity_kw_per_capita, colors=c("blue","red"), size=~capacity_mw
,hoverinfo = 'text',
text = ~paste('Country:', country, ' (', Country.Name, ')', '<br>Capacity MW:', capacity_mw, '<br>Population:', Population, '<br>Per Capita GDP:', PerCapitaGDP, '<br>Per Capita KW:', capacity_kw_per_capita)        
)

```

## And a plotly choropleth map
Power production capacity per country

```{r echo = FALSE, warning=FALSE}

# light grey boundaries
l <- list(color = toRGB("grey"), width = 0.5)

# specify map projection/options
g <- list(
  showframe = FALSE,
  showcoastlines = TRUE,
  projection = list(type = 'Mercator')
)

# mw_by_country <- mw_by_country[which(mw_by_country$country=="GRC"),]
# Warning!!! Choropleth maps do not appear in RStudio viewer
# You have to open it it a browser
plot_ly(mw_by_country, z = ~capacity_gw, locations = ~country, type = 'choropleth',
        color = ~capacity_gw, colors=c("blue","red"), marker = list(line = l),
        colorbar = list(tickprefix = '', title = 'Power Plants GWs')) %>%
  layout(title = 'Countries power capacity<br>Source:<a href="http://datasets.wri.org/dataset/globalpowerplantdatabase">Global Power Plant Database</a>',
         geo = g)

```

## Thank you

For this presentation, the following data sources were used:

* Global Power Plant Database <http://datasets.wri.org/dataset/globalpowerplantdatabase>
* Population, total from world bank <https://data.worldbank.org/indicator/SP.POP.TOTL>
* GDP per capita (current US$) from world bank <https://data.worldbank.org/indicator/NY.GDP.PCAP.CD>

